Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-08-21 paper.Rnw
small series of edits

Numerous methods have been proposed to provide explanations for black-box model predictions \citep{gilpin:2018, guidotti:2018, ming:2017, mohseni:2018, molnar:2019}. Some are specific to one type of model (e.g. \citep{simonyan:2013} and \citep{welling:2016}), and others are model-agnostic (e.g. \citep{fisher:2018} and \citep{strumbelj:2014}). In this paper, we focus on the model-agnostic method of LIME \citep{ribeiro:2016}.

\subsection{Conceptual Description of LIME}

@@

\autoref{fig:concept-plot-good} provides a visualization of this conceptual understanding of LIME. The two plots show the predictions from a hypothetical black-box model plotted against the two predictor variables used to fit the hypothetical model. The diamond shaped points represent a prediction of interest. A Gower distance metric \citep{gower:1971} is used to define locality such that the size of the points represent the inverse of the Gower distance raised to some value and indicate the proximity to the prediction of interest. Here, an exponent of \Sexpr{good_gower_power} is used to emphasize a very local region around the prediction of interest. A ridge regression model weighted by the proximity values is used as the explainer model with the black-box predictions as the response variable and standardized versions of Features 1 and 2 as predictor variables. Standardized features allow direct comparisons of the model coefficients. The explainer model is depicted by the black lines in the figure.

@@

\subsection{Motivation for Diagnosing LIME}

@@

\subsection{Structure of Paper}

The remainder of the paper is structured as follows. Section \ref{background} provides background and claims made by \citet{ribeiro:2016} about LIME. We introduce the suggested diagnostic plots in Section \ref{diagnostics}. Then in Section \ref{application}, we demonstrate the use of the diagnostics to assess LIME explanations for a random forest model fit to a forensics bullet matching dataset. Section \ref{discussion} concludes with a discussion on extensions and limitations of the diagnostic plots and concerns about LIME in regards to the claims made by \citet{ribeiro:2016} brought about by the visualization examples in this paper that agree with \citet{alvarezmelis:2018}, \citet{laugel:2018}, and \citet{molnar:2019}. The diagnostic plots included in this paper are created using the R package \emph{limeaid} \citep{goode:2020}. \kgc{(Would you like me to add you as an author on the limeaid package?)}

@@

LIME was introduced in 2016 by \citet{ribeiro:2016}. The original authors provide an implementation of LIME in a Python package\footnote{https://github.com/marcotcr/lime}. An adaption of the Python package in R is by Thomas Lin-Pedersen \citep{pedersen:2020}. In this paper, any details provided about the implementation of LIME are based on the R package.

As described by \citet{laugel:2018}, the general form of the LIME algorithm can be divided into three steps:

@@

During the application of LIME, the user must select various tuning parameter options: the number of features to return in the explanation, the simulation method, the feature selection method, and how the weights are computed. An overview of the options available for the tuning parameters is included in Appendix \ref{lime-details}.

@@

To demonstrate the visualizations, we generate an example dataset that will be referred to as the \data. The \data \ contains \Sexpr{dim(sine_data)[1]} observations with three features and one response variable. The features, $x_1$, $x_2$, and $x_3$, are randomly sampled from Unif(\Sexpr{min}, \Sexpr{max}), Unif(\Sexpr{min}, \Sexpr{max}), and $\mbox{N}(0,1)$ distributions, respectively. A binary response variable $y$ is  created using a rotated sine curve. In particular, let $x'_1=x_1\cos(\theta)-x_2\sin(\theta)$ and $x'_2=x_1\sin(\theta)+x_2\cos(\theta)$ where $\theta=-0.9$. Then $y$ is defined as
\begin{eqnarray}\label{eq:data}
  y=\begin{cases}
  \mbox{blue} & \mbox{ if } x'_2 > \sin\left(x'_1\right) \\
  \mbox{red} & \mbox{ if } x'_2 \le \sin\left(x'_1\right) \ . %\nolabel
  \end{cases}
\end{eqnarray}
Note that due to the creation of $y$ in this manner, $y$ is dependent on $x_1$ and $x_2$ and independent of $x_3$.

@@

We perform six applications of LIME with different tuning parameters to the random forest predictions from all observations in the sine data test set. To do this, we use the R package \emph{limeaid} \footnote{Available on GitHub at https://github.com/goodekat/limeaid} (\Sexpr{packageVersion("limeaid")}), which applies a forked version\footnote{https://github.com/goodekat/lime} of the development version of the R package \emph{lime} (\Sexpr{packageVersion("lime")}) \citep{pedersen:2020}. The forked version allows us to export internal values from \emph{lime}. The tuning parameters are as follows. For each application, we specify that LIME returns the top two features in the explanation, because we expect $x_1$ and $x_2$ to be the important features. Note that the complexity of an explanation goes hand in hand with the number of features selected to be included in the explanation. Setting the number of features to a small number will make the explanation simpler but not necessarily more correct. A quantile bin based simulation method is used for five of the LIME applications with the number of bins varying from 2 to 6 by application. We use 6 bins as the maximum, since the larger the number of bins, the more complex the explanation becomes. The sixth application of LIME uses a kernel density simulation method. The default methods for feature selection (forward selection) and the computation of the weights (Gower distance raised to an exponent of 1) are used for all applications.

\subsection{Explanation Scatterplots} \label{exp-scatter}

@@

plot_grid(sine_poi_exp, exp_scatter, align = "h")
@
\caption{(left) Visualization from the \emph{lime} R package of the LIME explanation for the \data \ prediction of interest. The bars represent the explainer model coefficients. (right) \emph{Explanation Scatterplot}. The points represent the simulated data colored by the random forest probabilities and sized by the assigned LIME weights. The prediction of interest is shown as the diamond shaped point. The explainer model indicator variables associated with $x_1$ and $x_2$ (quantile bins containing the prediction of interest) are depicted by the solid lines. The line colors represent the explainer model coefficient signs and indicate whether the feature supports a prediction of `blue' (blue lines) or supports a prediction of `red' (red lines). This figure shows that the quantile bins are not flexible enough to capture the relationship between the random forest predictions and the $x_1$ and $x_2$ values.}
\label{fig:sine-exp-scatter}
\end{figure*}

The \emph{explanation scatterplot} is a visual diagnostic for assessing the LIME claims of locality and fidelity for an individual explanation by juxtaposing the complex and explainer models in one plot. The format of an explanation scatterplot depends on the LIME simulation method. We introduce the explanation scatterplot here under the \emph{lime} R package default method in which the data are simulated uniformly from four quantile bins. In this scenario, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not. The indicator variables are used as the explainer model features. The explanation scatterplot achieves a juxtaposition of the complex and explainer models by plotting the LIME simulated data for two features in an explanation colored by the complex predictions overlaid by lines representing boundaries of the indicator variables used to fit the explainer model. The size of the points represents the weight assigned by LIME, and the color of the lines denote whether LIME indicates that a feature supports or contradicts a class prediction. Appendix \ref{exp-scatter_plus} addresses the explanation scatterplot formats in other LIME simulation scenarios.

To demonstrate an explanation scatterplot, we focus on the misclassified point indicated in Figure \ref{fig:sine-plot-data} by the diamond as the prediction of interest. First, consider the left plot in Figure \ref{fig:sine-exp-scatter}, which shows the \emph{lime} R package visualization of the explanation for the prediction of interest. The figure shows that the random forest returned a probability of \Sexpr{round(sine_poi_lime_default$label_prob[1], 2)} that the observation of interest belongs to category blue {(denoted as the ``label" in the figure).The lengths of the bars represent the explainer model coefficients associated with the indicator variables chosen by LIME as important. The color of the bar denotes the sign of the coefficient and whether the feature supports or contradicts a random forest classification of `blue'. The "explanation fit" value is the deviance ratio from the R package \emph{glmnet} \citep{simon:2011} for a ridge regression model. In other words, this is the $R^2$ value associated with the explainer model. In this case, it is \Sexpr{round(sine_poi_lime_default$model_r2[1], 2)} suggesting that the explainer model is not a good linear fit. However, it is commonly accepted that $R^2$ has limitations for accessing the quality of fit of a model \citep{sapra:2014}, and it should not be the only metric used for assessment of a model.

The explanation for the prediction of interest depicted in Figure \ref{fig:sine-exp-scatter} can be interpreted as follows. A random forest classification of blue is supported by the prediction of interest having a value of $x_2$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[1]], pattern = " ")[[1]][1]}, but the prediction of interest having a value of $x_1$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][1]} and less than or equal to \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][5]} provides support against a classification of blue. Since the weight associated with $x_2$ has a larger magnitude than the weight associated with $x_1$, LIME explains that the $x_1$ and $x_2$ locations of the prediction of interest provide more support for a random forest classification of blue over red. This explanation agrees with the random forest probability of \Sexpr{sine_poi_lime_default$label_prob[1]} for blue. Note that both models classify the observation incorrectly. Based on this plot alone, it is not possible to make an informed assessment of the explanation.

To assess the explanation, we turn to an explanation scatterplot shown as the right plot in Figure \ref{fig:sine-exp-scatter}. The points are the simulated values of $x_2$ versus $x_1$ colored by the random forest predictions and sized by the proximity weight used to fit the ridge regression explainer model. The explainer model is represented by the solid horizontal and vertical lines identifying the boundaries of the quantiles that contain the prediction of interest. The color of the lines indicate whether the explainer model coefficient is positive (blue) or negative (red). Thus, the $x_2$ coefficient is positive, so the $x_2$ value of the prediction of interest supports a random forest prediction of `blue', and the $x_1$ coefficient is negative, so the $x_1$ value of the prediction of interest contradicts a random forest prediction of `blue'. The prediction of interest is represented by the diamond shaped point.

@@

<<sine-feat-heat, out.width = '0.45\\textwidth', fig.width = 4, fig.height = 3.5>>=
plot_feature_heatmap(sine_lime_explain$explain,
                order_method = "PCA") +
  theme_bw(base_family = "Times", base_size = 10) +
  theme(legend.position = "bottom",
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        strip.background = element_rect(color = "white", fill = "white")) +
  labs(y = "Case")
@
\caption{\emph{Feature Heatmap}. An example feature heatmap of the explanations from the applications of LIME with different tuning parameters to the \data. The cases from the test set are plotted on the y-axis, and the tuning parameter values (simulation methods here) are included on the x-axis. The colors of the tiles indicate the feature selected by LIME for the corresponding case and tuning parameter value. The plot is faceted by the first features selected by LIME (top facet) and the second most important features (bottom facet). The column facets separate the kernel density method from the quantile bin methods. The vertical striping indicates that the LIME explanations are not consistent across tuning parameters.}
\label{fig:sine-feat-heat}
\end{figure}

@@

The largest limitation to the diagnostic visualizations is the dimensionality of the data shown, both in the number of dimensions or features as well as the number of observations. Fortunately, in the situation of LIME, both of these aspects are rather well controlled: LIME relies heavily on simulations to generate data scenarios that are close to the data observed but exhibits variability. Effects from overplotting should be relatively mild, because output from simulations is shown, which is expected to be (relatively) continuous \kgc{What do you mean by continuous here?}. In that respect, the diagnostics shown for the \data\ and in the bullet example are representative of what is expected. But in cases where overplotting does become problematic, the user could either simply reduce the size of the simulations or use some well-studied binning techniques in the visualizations, as discussed in \citet{carr:1987} \hh{reference to Millions book}

@@

\section*{Acknowledgments}

This is acknowledgment text. Provide text here.

@@

This is an author contribution text. This is an author contribution text. This is an author contribution text. This is an author contribution text. This is an author contribution text.

@@

\appendix

@@

% \textsc{\textbf{Ideas for describing proposed plots}}
% 
% \begin{itemize}
% \item start at the high level explanation (this is what we want to do and this is how we do it)
% \item go over a good and bad example
% \item include schematics of the plot first (good and bad) and then include the sine mini example version
% \item explain the expectation of the plot
% \end{itemize}
% 
% \textsc{\textbf{Comments for Editing}}
% 
% \begin{itemize}
% \item \hh{Generally: avoid 'can be'. Replace by 'is'.  }
% \item \hh{References like 'they', 'them' ... replace them by repeating the noun you are referring to to avoid any kind of ambiguity}
% \item \kgc{words to go back and make sure I am not using too often: ability, produce, understand}
% \item \kgc{decide on features or predictor variables}
% \item \hh{it's tuning parameters, not tunning} \kgc{Oops! I get that one wrong all of the time}
% \item \kgc{Adjust text sizes in plots so they all match}
% \item \kgc{Color scheme - comment from Heike:} \hh{I like the red-blue scheme for binary values, I also like the color scheme in the features heatmap. Generally papers and color don't go well together anyways, but we will solve that problem when we have to ... Most likely we will have to just pay the extra color fee}
% \item \kgc{Check that I am consistently referring to the perturbing as data simulation}
% \item \kgc{Clean up notation}
% \item \kgc{Referring to the linearity assumption:} \hh{Be a bit careful in the phrasing here - we can always approximate any function using a linear form (think Taylor expansion). The question is how big the error is.}
% \item \kgc{Make sure plots in the same figure are the same size}
% \item \kgc{Make sure I am distinguishing between RF predictions and probabilities correctly}
% \item \kgc{Use prediction of interest not case of interest}
% \item \kgc{Make sure I always treat the word 'data' as plural}
% \item \kgc{dataset or data set?}
% \item \kgc{scatterplot or scatter plot (check other plot names as well)}
% \item \kgc{choose whether to use the term feature or variable and make sure it is consistent throughout}
% \item \kgc{just include the details about LIME that are necessary to understand the plots and remove the rest to the appendix}
% \item \hh{avoid the use of implicit references like `this' and `that'. Make the reference explicit by adding what you are referring to, such as `this method', `that procedure'}
% \item \hh{make sure to use exact phrases. things like `LIME was developed in 2016' is factually questionable - but we know LIME was introduced in 2016. Also `the authors were interested in ...' implies that you know their intent. It's better to not guess any intent but stick to what we know.}
% \item \hh{`our` diagnostics ... you are using `our` quite often. It is good to claim work, but it is not good to claim things that we want others to use, because that is by definition excluding everybody but you. It's better to re-phrase with a focus on what you did. We introduce, we suggest, etc.}
% \item \kgc{check that I am always using present tense}
% \item \kgc{check that I am consistent in my use of the term black-box model}
% \end{itemize}

>>>>

Numerous methods have been proposed to provide explanations for black-box model predictions \citep{gilpin:2018, guidotti:2018, ming:2017, mohseni:2018, molnar:2019}. Some are specific to one type of model (e.g. \citep{simonyan:2013} and \citep{welling:2016}), and others are model-agnostic (e.g. \citep{fisher:2018} and \citep{strumbelj:2014}). In this paper, we focus on \hh{one specific} model-agnostic method: LIME \citet{ribeiro:2016} \hh{introduced by Ribeiro, Singh, and Guestrin in 2016}.

%\subsection{Conceptual Description of LIME}

@@

\autoref{fig:concept-plot-good} provides a visualization of this conceptual understanding of LIME. The two plots show the predictions from a hypothetical black-box model plotted against the two predictor variables used to fit the hypothetical model. The diamond shaped points represent a prediction of interest. A Gower distance metric \citep{gower:1971} is used to define locality such that the size of the points represent the inverse of the Gower distance raised to some value and indicate the proximity to the prediction of interest. \hh{In the example of \autoref{fig:concept-plot-good}} an exponent of \Sexpr{good_gower_power} is used to emphasize a very local region around the prediction of interest. A ridge regression model weighted by the proximity values is used as the explainer model with the black-box predictions as the response variable and standardized versions of \hh{two features in the data} % features Features 1 and~2 
as predictor variables. Standardized features allow direct comparisons of the model coefficients. The explainer model is depicted by the black lines in the figure.

@@

%\subsection{Motivation for Diagnosing LIME}

@@

%\subsection{Structure of Paper}

The remainder of the paper is structured as follows. Section \ref{background} provides background and claims made by \citet{ribeiro:2016} about LIME. We introduce the suggested diagnostic plots in Section \ref{diagnostics}. Then in Section \ref{application}, we demonstrate the use of the diagnostics to assess LIME explanations for a random forest model fit to a forensics bullet matching dataset. Section \ref{discussion} concludes with a discussion on extensions and limitations of the diagnostic plots and concerns about LIME in regards to the claims made by \citet{ribeiro:2016} brought about by the visualization examples in this paper that agree with \citet{alvarezmelis:2018}, \citet{laugel:2018}, and \citet{molnar:2019}. The diagnostic plots included in this paper are created using the R package \emph{limeaid} \citep{goode:2020}. %\kgc{(Would you like me to add you as an author on the limeaid package?)}\hh{I appreciated your offer, but limeaid is your package - I haven't written a single line :)}

@@

LIME was introduced in 2016 by \citet{ribeiro:2016}. The  authors provide an implementation of LIME in a Python package\footnote{https://github.com/marcotcr/lime}. An adaption of the Python package in R has been implemented and made available by Thomas Lin-Pedersen \citep{pedersen:2020}. The discussion of parameter choices and implementation details of LIME in this paper are based on the R package.

The general form of the LIME algorithm can be divided into three steps (see also \citep{laugel:2018}):

@@

During the application of LIME, the user is asked to select various tuning parameter options: the number of features to return in the explanation, the simulation method, the feature selection method, and how the weights are computed. An overview of the options available for the tuning parameters is included in Appendix~\ref{lime-details}.

@@

To demonstrate the visualizations, we generate an example dataset that will be referred to as the \data. The \data \ contains \Sexpr{dim(sine_data)[1]} observations with three features and one response variable. The features, $x_1$, $x_2$, and $x_3$, are randomly sampled from Unif(\Sexpr{min}, \Sexpr{max}), Unif(\Sexpr{min}, \Sexpr{max}), and $\mbox{N}(0,1)$ distributions, respectively. A binary response variable $y$ is  created using a rotated sine curve. In particular, let $x'_1=x_1\cos(\theta)-x_2\sin(\theta)$ and $x'_2=x_1\sin(\theta)+x_2\cos(\theta)$ where $\theta=-0.9$. Then $y$ is defined as
\begin{eqnarray}\label{eq:data}
  y=\begin{cases}
  \mbox{blue} & \mbox{ if } x'_2 > \sin\left(x'_1\right) \\
  \mbox{red} & \mbox{ if } x'_2 \le \sin\left(x'_1\right) \ . %\nolabel
  \end{cases}
\end{eqnarray}
Note that due to the creation of $y$ in this manner, $y$ is dependent on $x_1$ and $x_2$ and independent of $x_3$.
\hh{From the plots in \autoref{sine-plot-data} we see that the global relationship between response $y$ and features $x_1$ and $x_2$ is linear: the probability for label blue increases with the difference between features $x_2$ and $x_1$. Locally, the relationship between $y$ and features $x_2$ and $x_1$ varies a lot more around the line of identity. Here, the relationship  is determined by the sine waves. However, the sine is a good-natured function that can be approximated well linearly. }

@@

\hh{All runs of LIME in this paper are executed in}
a forked version\footnote{https://github.com/goodekat/lime} of the development version of the R package \emph{lime} (\Sexpr{packageVersion("lime")}) \citep{pedersen:2020}. 
The forked version \hh{is functionally indistinguishable from Pedersen's implementation but it} allows us to export internal values \hh{relevant for an assessment of the explainer}. 
The R package \emph{limeaid} \footnote{Available on GitHub at https://github.com/goodekat/limeaid} (\Sexpr{packageVersion("limeaid")}) implements diagnostic plots based on the output of the altered version of `lime`.

@@

plot_grid(sine_poi_exp, exp_scatter, align = "h") 
@
\caption{(left) Visualization from the \emph{lime} R package of the LIME explanation for the \data \ prediction of interest. The bars represent the explainer model coefficients. (right) \emph{Explanation Scatterplot}. The points represent the simulated data colored by the random forest probabilities and sized by the assigned LIME weights. \hh{XXX could you make the complex prediction **much** lighter for this example? The diamond and the lines are hard to see, but should be the focus.} The prediction of interest is shown as the diamond shaped point. The explainer model indicator variables associated with $x_1$ and $x_2$ (quantile bins containing the prediction of interest) are depicted by the solid lines. The line colors represent the explainer model coefficient signs and indicate whether the feature supports a prediction of `blue' (blue lines) or supports a prediction of `red' (red lines). This figure shows that the quantile bins are not flexible enough to capture the relationship between the random forest predictions and the $x_1$ and $x_2$ values.}
\label{fig:sine-exp-scatter}
\end{figure*}

A quantile bin based simulation method is used for five of the LIME applications with the number of bins varying from 2 to 6 by application. We use 6 bins as the maximum, \hh{because the complexity of the explanations increases with  the number of bins.} The sixth application of LIME uses a kernel density simulation method. The default methods for feature selection (forward selection) and the computation of the weights (Gower distance raised to an exponent of 1) are used for all applications.

\subsection{A LIME explanation}
\hh{XXX I've just pulled the description of the left hand side of figure 4 out of the next section.}
To demonstrate a LIME explanation, we focus on the misclassified point indicated in Figure \ref{fig:sine-plot-data} by the diamond as the prediction of interest. The left plot in Figure \ref{fig:sine-exp-scatter} shows a visualization of the explanation for the prediction of interest as suggested by Ribeiro et al and implemented in the \emph{lime} R package. The figure shows that the random forest returned a probability of \Sexpr{round(sine_poi_lime_default$label_prob[1], 2)} that the observation of interest belongs to category blue {(denoted as the ``label" in the figure).The lengths of the bars represent the explainer model coefficients associated with the indicator variables chosen by LIME as important. The color of the bar denotes the sign of the coefficient and whether the feature supports or contradicts a random forest classification of `blue'. The "explanation fit" value is the deviance ratio from the R package \emph{glmnet} \citep{simon:2011} for a ridge regression model. In other words, this is the $R^2$ value associated with the explainer model. In this case, it is \Sexpr{round(sine_poi_lime_default$model_r2[1], 2)} suggesting that the explainer model is not a good linear fit. However, it is commonly accepted that $R^2$ has limitations for assessing the quality of fit of a model \citep{sapra:2014}, and it should not be used as the only metric in a model assessment.

The explanation for the prediction of interest depicted in Figure \ref{fig:sine-exp-scatter} can be interpreted as follows. A random forest classification of blue is supported by the prediction of interest having a value of $x_2$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[1]], pattern = " ")[[1]][1]}, but the prediction of interest having a value of $x_1$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][1]} and less than or equal to \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][5]} provides support against a classification of blue. \hh{Because the support for blue by the value of feature $x_1$ outweighs the support for red by the value of feature $x_2$, the overall LIME explanation favors a label of blue for the prediction of interest.} %Since the weight associated with $x_2$ has a larger magnitude than the weight associated with $x_1$, LIME explains that the $x_1$ and $x_2$ locations of the prediction of interest provide more support for a random forest classification of blue over red.
This explanation agrees with the random forest probability of \Sexpr{sine_poi_lime_default$label_prob[1]} for blue. Note that both models classify the observation incorrectly. Based on the plot \hh{on the left of \autoref{fig:sine-exp-scatter}} alone, it is not possible to make an informed assessment of the explanation.

\subsection{Explanation Scatterplots} \label{exp-scatter}
\hh{XXX I think we could reduce some of the example for the specific example a bit, now that the LIME explanation is moved out, there is not that much need to repeat the general ideas.}

\hh{For a further assessment of the explainer model}, we turn to an \emph{explanation scatterplot}:
the \emph{explanation scatterplot} is a visual diagnostic for assessing the LIME claims of locality and fidelity for an individual explanation by juxtaposing the complex and explainer models in one plot. The format of an explanation scatterplot depends on the LIME simulation method. We introduce the explanation scatterplot here under the \emph{lime} R package default method in which the data are simulated uniformly from four quantile bins. In this scenario, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not. The indicator variables are used as the explainer model features.

The explanation scatterplot is built by plotting the LIME simulated data for the top two features identified by the explanation in a scatterplot and coloring these points by the  predictions from the complex model. The size of the points represents the weight assigned by LIME.
\hh{In order to show the LIME results for the observation of interest, }
 lines \hh{are drawn on top of the points. These lines } represent the boundaries of the indicator variables used to fit the explainer model. The color of the lines denote whether LIME indicates that a feature supports or contradicts a class prediction. Appendix \ref{exp-scatter_plus} addresses the explanation scatterplot formats in other LIME simulation scenarios.

\hh{An explanation scatterplot for the example of the previous section is shown on the right hand side of \autoref{fig:sine-exp-scatter}.}
 The points are the simulated values of $x_2$ versus $x_1$ colored by the random forest predictions and sized by the proximity weight used to fit the ridge regression explainer model. The explainer model is represented by the solid horizontal and vertical lines identifying the boundaries of the quantiles that contain the prediction of interest. The color of the lines indicate whether the explainer model coefficient is positive (blue) or negative (red). Thus, the $x_2$ coefficient is positive, so the $x_2$ value of the prediction of interest supports a random forest prediction of `blue', and the $x_1$ coefficient is negative, so the $x_1$ value of the prediction of interest contradicts a random forest prediction of `blue'. The prediction of interest is represented by the diamond shaped point.

@@

<<sine-feat-heat, out.width = '0.45\\textwidth', fig.width = 4, fig.height = 4>>=
plot_feature_heatmap(sine_lime_explain$explain,
                order_method = "PCA") +
  theme_bw(base_family = "Times", base_size = 10) +
  theme(legend.position = "bottom",
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        strip.background = element_rect(color = "white", fill = "white")) +
  labs(y = "Case")
@
\caption{\emph{Feature Heatmap}. An example feature heatmap of the explanations from the applications of LIME with different tuning parameters to the \data. The cases from the test set are plotted on the y-axis, and the tuning parameter values (simulation methods here) are included on the x-axis. The colors of the tiles indicate the feature selected by LIME for the corresponding case and tuning parameter value. The plot is faceted by the first features selected by LIME (top facet) and the second most important features (bottom facet). The column facets separate the kernel density method from the quantile bin methods. The vertical striping indicates that the LIME explanations are not consistent across tuning parameters.}
\label{fig:sine-feat-heat}
\end{figure}

@@

The largest limitation to the diagnostic visualizations is the dimensionality of the data shown, both in the number of dimensions or features as well as the number of observations. Fortunately, in the situation of LIME, both of these aspects are rather well controlled: LIME relies heavily on simulations to generate data scenarios that are close to the data observed but exhibits variability. Effects from overplotting should be relatively mild, because output from simulations is shown, which is expected to be (relatively) continuous \hh{such that overplotting only occurs for points with (relatively) similar values.} \kgc{What do you mean by continuous here?}. \hh{XXX Does that extra explanation help?} In that respect, the diagnostics shown for the \data\ and in the bullet example are representative of what is expected. But in cases where overplotting does become problematic, the user could either simply reduce the size of the simulations or use some well-studied binning techniques in the visualizations, as discussed for example in \citet{carr:1987} or \citet{gold}.

@@

\section*{Acknowledgments}
HH was partially funded by the Center for Statistics and Applications in Forensic Evidence (CSAFE) through Cooperative Agreement 70NANB20H019 between NIST and Iowa State University, which includes activities carried out at Carnegie Mellon University, Duke University, University of California Irvine, University of Virginia, West Virginia University, University of Pennsylvania, Swarthmore College and University of Nebraska, Lincoln.

@@

\hh{A taxonomy of author contributions is suggested by Elsevier - I put the link in an email
}

{\bf Katherine Goode, Heike Hofmann}: Conceptualization, Methodology, Investigation, Writing- Reviewing and Editing.
{\bf Katherine Goode}: Writing Initial Draft, Software.

@@

% \textsc{\textbf{Ideas for describing proposed plots}}
% 
% \begin{itemize}
% \item start at the high level explanation (this is what we want to do and this is how we do it)
% \item go over a good and bad example
% \item include schematics of the plot first (good and bad) and then include the sine mini example version
% \item explain the expectation of the plot
% \end{itemize}
% 
% \textsc{\textbf{Comments for Editing}}
% 
% \begin{itemize}
% \item \hh{Generally: avoid 'can be'. Replace by 'is'.  }
% \item \hh{References like 'they', 'them' ... replace them by repeating the noun you are referring to to avoid any kind of ambiguity}
% \item \kgc{words to go back and make sure I am not using too often: ability, produce, understand}
% \item \kgc{decide on features or predictor variables}
% \item \hh{it's tuning parameters, not tunning} \kgc{Oops! I get that one wrong all of the time}
% \item \kgc{Adjust text sizes in plots so they all match}
% \item \kgc{Color scheme - comment from Heike:} \hh{I like the red-blue scheme for binary values, I also like the color scheme in the features heatmap. Generally papers and color don't go well together anyways, but we will solve that problem when we have to ... Most likely we will have to just pay the extra color fee}
% \item \kgc{Check that I am consistently referring to the perturbing as data simulation}
% \item \kgc{Clean up notation}
% \item \kgc{Referring to the linearity assumption:} \hh{Be a bit careful in the phrasing here - we can always approximate any function using a linear form (think Taylor expansion). The question is how big the error is.}
% \item \kgc{Make sure plots in the same figure are the same size}
% \item \kgc{Make sure I am distinguishing between RF predictions and probabilities correctly}
% \item \kgc{Use prediction of interest not case of interest}
% \item \kgc{Make sure I always treat the word 'data' as plural}
% \item \kgc{dataset or data set?}
% \item \kgc{scatterplot or scatter plot (check other plot names as well)}
% \item \kgc{choose whether to use the term feature or variable and make sure it is consistent throughout}
% \item \kgc{just include the details about LIME that are necessary to understand the plots and remove the rest to the appendix}
% \item \hh{avoid the use of implicit references like `this' and `that'. Make the reference explicit by adding what you are referring to, such as `this method', `that procedure'}
% \item \hh{make sure to use exact phrases. things like `LIME was developed in 2016' is factually questionable - but we know LIME was introduced in 2016. Also `the authors were interested in ...' implies that you know their intent. It's better to not guess any intent but stick to what we know.}
% \item \hh{`our` diagnostics ... you are using `our` quite often. It is good to claim work, but it is not good to claim things that we want others to use, because that is by definition excluding everybody but you. It's better to re-phrase with a focus on what you did. We introduce, we suggest, etc.}
% \item \kgc{check that I am always using present tense}
% \item \kgc{check that I am consistent in my use of the term black-box model}
% \end{itemize}
\newpage
\appendix

@@
